Stack Safety as a Security Property

### 2020-06-24 main.tex
Better explanation (still brief) of how heap safety should work

    While these ideas are here presented in a stack-centric style, they could
    be extended to heap safety in a system extended with a heap. Heap safety,
    like stack safety, may be framed as a form of noninterference
    [cite Meaning of Memory Safety]. As in stack safety, the mapping from
    components to security labels would be dynamic, with any heap data
    unreachable from the stack frame in a given state treated as high
    confidentiality and high integrity. This would require updating the contour
    at each step.

>>>>

    While these ideas are here presented in a stack-centric style, they could
    be extended to heap safety in a system extended with a heap. Heap safety,
    like stack safety, may be framed as a form of noninterference
    [cite Meaning of Memory Safety]. For each certain component marked as
    containing a valid pointer to a heap object, we can propagate that
    validity when the pointer moves or is used in pointer arithmetic. Heap
    objects to which a valid pointer is in a register are reachable, and
    treated as low confidentiality and low integrity.
